Rapid cycleway prioritisation tool

### 2020-06-08 code/index.Rmd
Shorten intro

```{r pkg, include=FALSE}
library(sf)
library(tidyverse)
library(tmap)
tmap_mode("view")
```

@@

The [rapid cycleway prioritisation tool](https://www.cyipt.bike/rapid/) helps identify promising locations for road space reallocation in England.
The tool provides an evidence base to support investment in cycling infrastructure, in response to new pressures placed on transport and public health systems by the COVID-19 crisis, at local and regional levels.
The rational for the tool is that, in the context of COVID-19, big decisions around where to prioritise investment on the road network need to be made quickly.
The tool provides a 'first pass' assessment of the existing road network to help focus planning attention on options that are likely to have sufficient space for new infrastructure in places where there is high latent demand.

@@

```{r}
dn = "popupCycleways/v1" # dirctory name
built_regions = list.files(dn)
regions = regions %>% 
  filter(stringr::str_detect(string = Name, "Scilly", negate = TRUE))
regions %>%
  sf::st_drop_geometry() %>%
  # filter(html_name %in% built_regions) %>% 
  select(Name, Level, url) %>% 
  arrange(Name) %>% 
  DT::datatable(escape = -4)
```

>>>>

```{r pkg, include=FALSE}
library(sf)
library(tidyverse)
library(dplyr)
library(tmap)
tmap_mode("view")
```

@@

The [rapid cycleway prioritisation tool](https://www.cyipt.bike/rapid/) helps identify promising locations for road space reallocation in England.
The tool provides an evidence base to support investment in cycling infrastructure, in response to new pressures placed on transport and public health systems by the COVID-19 crisis, at local and regional levels.
The rational for the tool is that, in the context of COVID-19, big decisions around where to prioritise investment on the road network need to be made quickly.
The tool provides a ‘first pass’ assessment of promising locations for new cycleways which have high latent demand for cycling and where road space can be reallocated whilst maintaining two-way traffic flows for motorists.

@@

```{r}
dn = "popupCycleways/v1.1" # dirctory name
built_regions = list.files(dn)
regions = regions %>% 
  filter(stringr::str_detect(string = Name, "Scilly", negate = TRUE))
regions %>%
  sf::st_drop_geometry() %>%
  # filter(html_name %in% built_regions) %>% 
  select(Name, Level, url) %>% 
  arrange(Name) %>% 
  DT::datatable(escape = -4)
```
